The robot who pretend-played with me

### 2017-04-06 paper.tex
Desc of the freeplay sandbox + brainstorm on research questions

\begin{itemize}
    \item Can I have real fun playing with my robot?
    \item A Window Onto Your Mind: Playful Robots Leveraging Attention to
        Predict Actions
    \item Playing Like your Friend: Dealing with the High Dimensionality of
        Real-World Social Dynamic

@@

    We study this effect in a high-dimensional social interaction situation based on
    free dramatic play: pairs of children (4-7 years old) or robot and child are
    invited to freely interact with characters and items on an interactive
    table, telling and acting stories with no explicit preset goal.

@@

\section{Methodology: Social Interaction during Free Play}

@@

\begin{itemize}
    \item storytelling
    \item creative play
    \item pretend play
\end{itemize}

@@

@@

@@

\subsection{What Does the Model Predict?}

>>>>

\begin{itemize}
    \item Can I have real fun playing with my robot?
    \item A Robot Which is Fun to Play With: Leveraging AI to Participate in Complex
        Social Situations
    \item A Window Onto Your Mind: Playful Robots Leveraging Attention to
        Predict Actions
    \item Playing Like your Friend: Dealing with the High Dimensionality of
        Real-World Social Dynamic

@@

    We study this effect in a high-dimensional social interaction situation based on
    free dramatic play: pairs of children (4-7 years old) or robot and child are
    invited to freely interact with characters and items on an interactive
    table, telling and acting stories with no explicit goal set in advance.

@@

\section{Social Interaction during Free Play}

\subsection{A novel methodology}

@@

\begin{itemize}
    \item dramatic play
    \item storytelling
    \item creative play
    \item pretend play
\end{itemize}

@@

\subsection{Implementation}

The sandbox is implemented using mainly two frameworks: the Qt's \emph{QtQuick} framework
for the graphical interface of the game, and the \emph{Robot Operating System}
(ROS) for the modular implementation of the data processing and behaviour
generation pipelines.

Figure~\ref{fig|architecture} presents the software architecture of the sandbox.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{freeplay-sandbox-architecture}
\label{fig|architecture}
\caption{Architecture of the free play sandbox. Yellow nodes represent
    hardware (cameras and robot); purple nodes relate to the game interface;
    red nodes manage the robot; the green node implements the game policy (when
    the robot is playing); blue nodes relates to visual attention tracking.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{rviz-sandtray}
    \caption{The freeplay sandbox, viewed at runtime within ROS RViz
    visualisation tool.}
    \label{fig|rviz}
\end{figure}

\section{Research Questions and Hypotheses}

The mechanisms underlying the social interactions happening during free play
raise important questions for social robotics.

\subsection{Game Dynamics}

\begin{itemize}
    \item do we observe a sequence of sub-games?
    \item how are these sub-games initiated?
    \item how does A keep track of what B is playing at?
    \item how do we segment the action flow into meaningful play situations?
\end{itemize}

\subsection{Social Dynamics}

\begin{itemize}
    \item does a ``social protocol'' establish?
    \item if so, what are these social rules?
    \item implicit vs explicit rule setting?
    \item what interaction modalities (or combination thereof) are relied upon
        to establish and maintain this ``social protocol''?
\end{itemize}

\subsection{Mental representations}

\begin{itemize}
    \item Does A know what B is thinking of at time t?
    \item Do the participants perform explicit grounding of their respective mental models
        (ie, ask the other one what she is doing/thinking/planning to do?)
    \item How does the implicit grounding take place? attention tracking?
    \item Do we need at all to know what the other intends to do to actually
        collaborate? surface alignment vs deep grounding
    \item Procedural (how do you do it?) vs Semantic
        grounding (what are you doing? playing at?)
\end{itemize}

\subsection{Interplay between these questions}

\begin{figure}
\centering

\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
                font=\sffamily,
                >=latex,
                every edge/.style={draw, very thick},
                node/.style={draw, rounded corners, align=center, inner sep=5pt, fill=black!20},
                label/.style={midway, align=center, font=\scriptsize\sffamily, fill=white}]

    %%% NODES
    \node [node] (mentalrepresentations) {Mental Representations};
    \node [above left=of mentalrepresentations] (gameactions) {game actions};
    \node [node, above left=of gameactions] (gamedynamics) {Game dynamics};
    \node [above right=of mentalrepresentations] (socialactions) {social actions};
    \node [node, above right=of socialactions ] (socialdynamics) {Social Dynamics};

    %%% CONNECTIONS
    \path (gamedynamics) edge [<->, dashed] node[label, above] {?}(socialdynamics);
    \path (gamedynamics) edge [<-, bend right] node[label] {mediate}(gameactions);
    \path (socialactions) edge [->, bend left] node[label] {reflect}(mentalrepresentations);
    \path (socialactions) edge [->, dashed] node[label,above] {?}(gamedynamics);
    \path (gameactions) edge [->, dashed] node[label,above] {?}(socialdynamics);
    \path (gameactions) edge [->, bend right] node[label] {reflect}(mentalrepresentations);
    \path (socialdynamics) edge [<-, bend left] node[label] {shape}(socialactions);

\end{tikzpicture}
}
\label{fig|researchquestions}
\caption{Game dynamics, social dynamics and mental representations are linked
    with each other through social actions (implicit and explicit communication)
    and actions on the environment (mainly game actions)}
\end{figure}

\subsection{Hypotheses}

\section{Experiments}

\subsection{Procedure}

@@

\subsection{Results}

@@
